---
output:
  md_document:
    variant: markdown_github
---

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(devtools)
library(monitoRingrepoRt)

knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = TRUE, fig.align = 'center')

```

# mointeRing repoRt 0.0.0.9000

[Edgar Zamora \| Twitter: `@Edgar_Zamora_`](https://twitter.com/Edgar_Zamora_)

The `mointoRingrepoRt` package is a collection of functions that will aid in the production of the Annual [Mission Fulfillment Monitoring Report](https://www.bigbend.edu/monitoring-reports/) that is produced by the Big Bend [Institutional Research and Planning Department](https://www.bigbend.edu/information-center/institutional-research-planning/).

To install the `mointoRingrepoRt` package run the following code:

```{r installation, eval=FALSE}
devtools::install_github("Edgar-Zamora/mointoRingrepoRt")
```


# Student Succcess

## Total Student FTE (Full-time Equivalent)

The `program_area()` is a function that will return the FTE counts for each program area at Big Bend. The only argument that is present within the function is `last_yr` which asks that you include the latest complete year of data in the data warehouse. Doing so is necessary because if not than the graphic and table will reflect quarterly data instead of annual data. 


By setting the `last_yr` argument to `"B90"` I am telling the function to return data regarding program FTE's starting in "B23" to "B90". The lower limit of "B23" is automatically defined and will not change. 

```{r program_area_fte, eval=FALSE}

program_area_fte(last_yr = "B90")

```

## Enrollment by modality

The `modeality_fte()` function will return a dataframe containing the FTE for each modality of a class. The classification of what constitutes certain modalities is defined within the R function. The only argument that needs defining is the `last_yr` one, which asks that you include the latest complete year of data in the data warehouse. Doing so is necessary because if not than the graphic and table will reflect quarterly data instead of annual data. 

```{r modality, eval=FALSE}

modality_fte(last_yr = "B90")

```






